Disease and climate effects on individuals drive post-reintroduction

### 2018-09-04 article.Rmd
updating caption to account for A and B panels
minor tweaks ot figs

Despite the two study populations being 12 km apart, mean Bd loads among infected adults varied synchronously between populations. 
After initial introduction in 2006 or 2008, mean loads at both sites were typically between 1,000 and 10,000 copies, with a reduction in mean Bd load during the year following the first introduction (Figure \ref{mean-bd-loads}A). 
Thereafter, loads were relatively low and stable through 2012. 
At both sites mean loads were uncharacteristically low in 2013 but increased in subsequent years until reaching a peak in 2016. 
Mean Bd loads at Subalpine tended to be higher than at Alpine, particularly in the period from 2015 - 2017. 
The estimated correlation over time between mean log Bd loads at the two study sites was `r median(unlist(bd_load_correlations)) %>% round(n_digit)` (`r quantile(unlist(bd_load_correlations), .05) %>% round(n_digit)`, `r quantile(unlist(bd_load_correlations), .95) %>% round(n_digit)`). 
This correlation was not due to a shared response to winter severity because winter severity did not influence Bd load at either site (at Alpine $\beta^{(\mu)}$: `r beta_z_df %>% filter(site == "Alpine") %>% select(med) %>% df2num` (`r beta_z_df %>% filter(site == "Alpine") %>% select(lo) %>% df2num`, `r beta_z_df %>% filter(site == "Alpine") %>% select(hi) %>% df2num`), at Subalpine $\beta^{(\mu)}$: `r beta_z_df %>% filter(site == "Subalpine") %>% select(med) %>% df2num` (`r beta_z_df %>% filter(site == "Subalpine") %>% select(lo) %>% df2num`, `r beta_z_df %>% filter(site == "Subalpine") %>% select(hi) %>% df2num`).

@@

\textit{Batrachochytrium dendrobatidis} (Bd) infection loads over time. 
Observed load values from skin swabs are shown as points on a log10 scale, colored by site. 
The estimated average Bd infection load is shown as a line (posterior median) with a 90\% credible interval ribbon.

>>>>

Despite the two study populations being 12 km apart, mean Bd loads among infected adults varied synchronously between populations. 
After initial introduction in 2006 or 2008, mean loads at both sites were typically between 1,000 and 10,000 copies, with a reduction in mean Bd load during the year following the first introduction (Figure \ref{mean-bd-loads}A). 
Thereafter, loads were relatively low and stable through 2012. 
At both sites mean loads were uncharacteristically low in 2013 but increased in subsequent years until reaching a peak in 2016. 
Mean Bd loads at Subalpine tended to be higher than at Alpine, particularly in the period from 2015 - 2017. 
The estimated correlation over time between mean log Bd loads at the two study sites was `r median(unlist(bd_load_correlations)) %>% round(n_digit)` (`r quantile(unlist(bd_load_correlations), .05) %>% round(n_digit)`, `r quantile(unlist(bd_load_correlations), .95) %>% round(n_digit)`)  (Figure \ref{mean-bd-loads}B). 
This correlation was not due to a shared response to winter severity because winter severity did not influence Bd load at either site (at Alpine $\beta^{(\mu)}$: `r beta_z_df %>% filter(site == "Alpine") %>% select(med) %>% df2num` (`r beta_z_df %>% filter(site == "Alpine") %>% select(lo) %>% df2num`, `r beta_z_df %>% filter(site == "Alpine") %>% select(hi) %>% df2num`), at Subalpine $\beta^{(\mu)}$: `r beta_z_df %>% filter(site == "Subalpine") %>% select(med) %>% df2num` (`r beta_z_df %>% filter(site == "Subalpine") %>% select(lo) %>% df2num`, `r beta_z_df %>% filter(site == "Subalpine") %>% select(hi) %>% df2num`).

@@

A. \textit{Batrachochytrium dendrobatidis} (Bd) infection loads over time. 
Observed load values from skin swabs are shown as points on a log10 scale, colored by site. 
The estimated average Bd infection load is shown as a line (posterior median) with a 90\% credible interval ribbon.
B. Estimated Bd infection prevalence over time, with posterior medians shown as lines and 90\% credible intervals shown as shaded ribbons.
